Wikipedia Text Mining and Surprisal Analysis

### 2019-07-16 surprisal/WALS_features.Rmd

```{r read in data}
wkpd <- read.csv(here("Data/wikipedia_unigrams.csv"))
LANGUAGES <- wkpd$language

wals <- read.csv(here("Data/wals.csv"))
feature_names <- read_feather(here("Wikipedia/feature_names.feather"))
```

@@

>>>>

```{r read in data}
wals <- read_csv(here("Data/wals.csv"))
feature_names <- read_feather(here("Wikipedia/feature_names.feather"))

wiki <- read_csv(here("Data/relative_ngrams.csv"))
LANGUAGES <- wiki %>% pull(language) %>% unique()
```

@@

## Errata

```{r cleaning}
wiki <- read_feather(here("Data/relative_ngrams.feather"))
wiki %>% 
  group_by(language) %>% 
  mutate(order = 1:n()) %>% 
  ungroup() %>% 
  filter(order <= 15) %>% 
  select(-order) %>%
  select(language, gram, estimate, cut) %>% 
  spread(cut, estimate) %>% 
  rename(Slope1 =`1`, Slope2 =`2`, Slope3 =`3`, Slope4 =`4`, Slope5 =`5`) %>%
  write_csv(here("Data/relative_ngrams.csv"))
```

### 2019-07-16 surprisal/wiki_surprisal.Rmd

wf <- read_csv(here("Data/wals.csv")) 
feature_names <- read_feather(here("Wikipedia/feature_names.feather"))
```

>>>>

FEATURES <- c(1:144)
for (i in c(1:length(FEATURES))) {
  FEATURES[i] <- paste(FEATURES[i], "A", sep = "")
} #get all word order WALS features in correct syntax

wals_isos <- wals %>%
  mutate(iso = iso.gltc(glottocode)) %>%
  select(-glottocode)

wiki_isos <- read_csv(here("Wikipedia/wiki_isos.csv")) %>%
  clean_names() %>%
  select(x639_1, x639_3)

wiki_langs <- fromJSON(here("/Wikipedia/language_dict.json")) %>%
  as_tibble() %>%
  gather(language, x639_1) %>%
  left_join(wiki_isos)

%>%
  left_join(wals_isos) %>%
  filter(is.na(wals.code)) %>%
  View()

wf <- wals.feature(FEATURES)

write_csv(wf, here("Data/wals.csv"))
```

```{r load-wals, eval = T}
wf <- read_csv(here("Data/wals.csv"))
